Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-05-19 arxiv/template.tex
better arxiv template

\usepackage{PRIMEarxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{fancyhdr}       % header
\usepackage{graphicx}       % graphics
\graphicspath{{media/}}     % organize your images and other figures under media/ folder

%Header
\pagestyle{fancy}
\thispagestyle{empty}
\rhead{ \textit{ }}

% Update your Headers here
\fancyhead[LO]{Proper length as a radial coordinate in the Schwarzschild metric}
% \fancyhead[RE]{Firstauthor and Secondauthor} % Firstauthor et al. if more than 2 - must use \documentclass[twoside]{article}

%% Title
\title{A template for Arxiv Style
%%%% Cite as
%%%% Update your official citation here when published 
\thanks{\textit{\underline{Citation}}: 
\textbf{Authors. Title. Pages.... DOI:000000/11111.}} 
}

\author{
  Robin K. S. Hankin \\
Auckland University of Technology \\
Auckland, New Zealand\\
  \texttt{hankin.robin@gmail.com} 
}

@@

% keywords can be removed
\keywords{Black holes\and Schwarzschild metric\and proper distance}

\section{Introduction}

The Schwarzschild metric is usually written

\begin{equation}
  ds^2=-dt^2\left(1-\frac{2GM}{c^2r}\right)
  +\frac{dr^2}{\left(1-\frac{2GM}{c^2r}\right)} + r^2(\sin^2\theta
  d\phi^2 + d\theta^2)
\end{equation}

@@

Hankin \cite{hankin2021} shows that

@@

\section{Conclusion}
Your conclusion here

%Bibliography
\bibliographystyle{unsrt}  
\bibliography{references}

>>>>

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{lipsum}         % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\title{Proper radial distance as a coordinate in the Schwarzschild metric}

% Here you can change the date presented in the paper title
%\date{September 9, 1985}
% Or remove it
%\date{}

\author{ \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Robin K. S. Hankin}\thanks{Use footnote for providing further
		information about author (webpage, alternative
		address)---\emph{not} for acknowledging funding agencies.} \\
              AUT University\\
              Auckland, New Zealand\\
	\texttt{hankin.robin@gmail.com} \\
}

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{Proper radial distance}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={Proper radial distance as a coordinate in the Schwarzschild metric}
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Robin K. S.~Hankin}
pdfkeywords={First keyword, Second keyword, More},
}

@@

% keywords can be removed
\keywords{First keyword \and Second keyword \and More}

\section{Introduction}
The Schwarzschild metric is usually written

\begin{equation}
  ds^2=-dt^2\left(1-\frac{2GM}{c^2r}\right)
<  +\frac{dr^2}{\left(1-\frac{2GM}{c^2r}\right)} + r^2(\sin^2\theta
  d\phi^2 + d\theta^2)
\end{equation}

@@

\cite{hankin2021} shows that

\citep{hankin2021} shows that

\citet{hankin2021} shows that

\cite{hankin2020}

@@

\bibliographystyle{unsrtnat}
\bibliography{references}
